Stateless Model Checking with Data-Race Preemption Points

### 2015-11-20 pldi-16/soundness.tex
name convergence lemma in paper

\newcommand\ppnext[1]{\ensuremath{\mathsf{next}(#1)}}
\newcommand\ppinstr[1]{\ensuremath{\mathsf{instr}(#1)}}
\newcommand\ppothers[1]{\ensuremath{\mathsf{others}(#1)}}
\begin{theorem}
If a bug can be exposed by any thread interleaving possible by preempting on all instructions during a specific test,
Iterative Deepening will eventually test an equivalent interleaving which exposes the same bug.
\end{theorem}
\begin{proof}
The proof has two parts:
first, we show that preempting on data-racing instructions and synchronization API boundaries suffices to test all possible program behavior;
second, we show that Iterative Deepening will eventually detect all such data races.
Given a PP $p$, let $\ppnext{p}$ denote the next transition after $p$ executed by the thread which ran immediately before $p$,
let $\ppinstr{p}$ denote the first instruction of $\ppnext{p}$,
and let $\ppothers{p}$ denote the transitions by other threads between $p$ and $\ppnext{p}$.

@@

\begin{definition}[Reachability]
A data race candidate, and its associated PPs, are reachable if it will be identified by an MC configured to preempt only on already-reachable PPs.
\end{definition}
Initially, the statically-available synchronization API PPs are reachable. Reachability of data-race PPs is transitive.
\begin{lemma}[Saturation of data-race PPs]
	Given any interleaving comprising only data-race PPs and synchronization API PPs, all involved PPs are reachable.
	\label{lem:saturation}
\end{lemma}

>>>>

\newcommand\ppnext[1]{\ensuremath{\mathsf{next}(#1)}}
\newcommand\ppinstr[1]{\ensuremath{\mathsf{instr}(#1)}}
\newcommand\ppothers[1]{\ensuremath{\mathsf{others}(#1)}}
\begin{theorem}[Convergence]
If a bug can be exposed by any thread interleaving possible by preempting on all instructions during a specific test,
Iterative Deepening will eventually test an equivalent interleaving which exposes the same bug.
\end{theorem}
\begin{proof}
The proof has two parts:
first, we show that preempting on data-racing instructions and synchronization API boundaries suffices to test all possible program behavior;
second, we show that Iterative Deepening will eventually detect all such data races.
Given a PP $p$, let $\ppnext{p}$ denote the next transition after $p$ executed by the thread which ran immediately before $p$,
let $\ppinstr{p}$ denote the first instruction of $\ppnext{p}$,
and let $\ppothers{p}$ denote the transitions by other threads between $p$ and $\ppnext{p}$.

@@

\begin{definition}[Reachability]
A data race candidate, and its associated PPs, are reachable if it will be identified by an MC configured to preempt only on already-reachable PPs.
\end{definition}
Initially, the statically-available synchronization API PPs are reachable. Reachability of data-race PPs is transitive.

\begin{lemma}[Saturation of data-race PPs]
	Given any interleaving comprising only data-race PPs and synchronization API PPs, all involved PPs are reachable.
	\label{lem:saturation}
\end{lemma}
